---
title: "R Notebook"
author: Yanan Wu
output:  
  html_notebook:
    toc: TRUE
    toc_float: TRUE
---

##Introduction
###Implements various mainstream and specialised changepoint methods for finding single and multiple changepoints within data.


##Calling R Function Defined In Other Scripts
### Calling Function directly from the folder
```{r,message=FALSE, comment= NA}
setwd(".")

source("change_point.R")
source("valid_lake_level.R")
source("total_month.R")
source("get_month_period.R")
source("get_level.R")
```

##Display Data
###Choose the data using Filte_valid_data function and get_water_level function
```{r, message=FALSE, comment= NA}
validdata <- Filte_Valid_data(2)
validdata
level <- get_water_leve(validdata)
level
```

##Create year month
###Create time series year month
```{r, message = FALSE, comment= NA}
total <- create_month_year(1990, 2016, 5, 10) # run two times(first time download the package)
yearvalue <- get_the_time_period(validdata, total)
yearvalue
```

## Visualize Change Point 
### Display the change point and lake level change pattern
```{r, echo=FALSE, message=FALSE, comment= NA, fig.width=9}
change_point(level, yearvalue)
```
